APPM 3310 Project\\\Large{Static Analysis of Truss Systems}

### 2016-04-28 paper.tex
Add code and input files.

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{float}

@@

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{float}
\usepackage{appendix}
\usepackage{geometry}

\usepackage{bera}
\usepackage{listings}
\usepackage{xcolor}
\colorlet{punct}{red!60!black}
\definecolor{background}{HTML}{EEEEEE}
\definecolor{delim}{RGB}{20,105,176}
\colorlet{numb}{magenta!60!black}
\lstdefinelanguage{json}{
    basicstyle=\normalfont\ttfamily,
    numbers=left,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    frame=lines,
    backgroundcolor=\color{background},
    literate=
     *{0}{{{\color{numb}0}}}{1}
      {1}{{{\color{numb}1}}}{1}
      {2}{{{\color{numb}2}}}{1}
      {3}{{{\color{numb}3}}}{1}
      {4}{{{\color{numb}4}}}{1}
      {5}{{{\color{numb}5}}}{1}
      {6}{{{\color{numb}6}}}{1}
      {7}{{{\color{numb}7}}}{1}
      {8}{{{\color{numb}8}}}{1}
      {9}{{{\color{numb}9}}}{1}
      {:}{{{\color{punct}{:}}}}{1}
      {,}{{{\color{punct}{,}}}}{1}
      {\{}{{{\color{delim}{\{}}}}{1}
      {\}}{{{\color{delim}{\}}}}}{1}
      {[}{{{\color{delim}{[}}}}{1}
      {]}{{{\color{delim}{]}}}}{1},
}
\usepackage[framed, numbered]{matlab-prettifier}

@@

\newgeometry{top=1in, bottom=1in, left=1in, right=1in}
\begin{appendices}

\section{Code}

This is the code from \cite{shannon2016}.

\subsection{config.m}\label{app:config.m}
\lstinputlisting[style=Matlab-editor]{code/config.m}

\subsection{lint.m}\label{app:lint.m}
\lstinputlisting[style=Matlab-editor]{code/lint.m}

\subsection{save\_figure.m}\label{app:save_figure.m}
\lstinputlisting[style=Matlab-editor]{code/save_figure.m}

\subsection{save\_tables.m}\label{app:save_tables.m}
\lstinputlisting[style=Matlab-editor]{code/save_tables.m}

\subsection{truss.m}\label{app:truss.m}
\lstinputlisting[style=Matlab-editor]{code/truss.m}

\subsection{libs/colormap\_lookup.m}\label{app:libs/colormap_lookup.m}
\lstinputlisting[style=Matlab-editor]{code/libs/colormap_lookup.m}

\subsection{libs/draw\_arrow.m}\label{app:libs/draw_arrow.m}
\lstinputlisting[style=Matlab-editor]{code/libs/draw_arrow.m}

\subsection{libs/element\_freedom\_table.m}\label{app:libs/element_freedom_table.m}
\lstinputlisting[style=Matlab-editor]{code/libs/element_freedom_table.m}

\subsection{libs/force\_vector.m}\label{app:libs/force_vector.m}
\lstinputlisting[style=Matlab-editor]{code/libs/force_vector.m}

\subsection{libs/global\_stiffness\_matrix.m}\label{app:libs/global_stiffness_matrix.m}
\lstinputlisting[style=Matlab-editor]{code/libs/global_stiffness_matrix.m}

\subsection{libs/load\_model.m}\label{app:libs/load_model.m}
\lstinputlisting[style=Matlab-editor]{code/libs/load_model.m}

\subsection{libs/local\_stiffness\_matrix.m}\label{app:libs/local_stiffness_matrix.m}
\lstinputlisting[style=Matlab-editor]{code/libs/local_stiffness_matrix.m}

\subsection{libs/master\_stiffness\_matrix.m}\label{app:libs/master_stiffness_matrix.m}
\lstinputlisting[style=Matlab-editor]{code/libs/master_stiffness_matrix.m}

\subsection{libs/modify\_stiffness\_matrix.m}\label{app:libs/modify_stiffness_matrix.m}
\lstinputlisting[style=Matlab-editor]{code/libs/modify_stiffness_matrix.m}

\subsection{libs/parse\_json.m}\label{app:libs/parse_json.m}
\url{http://www.mathworks.com/matlabcentral/fileexchange/20565-json-parser}

\subsection{libs/plot\_model.m}\label{app:libs/plot_model.m}
\lstinputlisting[style=Matlab-editor]{code/libs/plot_model.m}

\subsection{libs/solve\_displacements.m}\label{app:libs/solve_displacements.m}
\lstinputlisting[style=Matlab-editor]{code/libs/solve_displacements.m}

\subsection{libs/solve\_forces.m}\label{app:libs/solve_forces.m}
\lstinputlisting[style=Matlab-editor]{code/libs/solve_forces.m}

\subsection{libs/solve\_model.m}\label{app:libs/solve_model.m}
\lstinputlisting[style=Matlab-editor]{code/libs/solve_model.m}

\subsection{libs/solve\_stresses.m}\label{app:libs/solve_stresses.m}
\lstinputlisting[style=Matlab-editor]{code/libs/solve_stresses.m}

\subsection{libs/transformation\_matrix.m}\label{app:libs/transformation_matrix.m}
\lstinputlisting[style=Matlab-editor]{code/libs/transformation_matrix.m}

\section{Input Files}

\subsection{samples/sample\_001.json}\label{app:samples/sample_001.json}
\lstinputlisting[language=json]{code/samples/sample_001.json}

\subsection{samples/sample\_002.json}\label{app:samples/sample_002.json}
\lstinputlisting[language=json]{code/samples/sample_002.json}

\subsection{samples/sample\_003.json}\label{app:samples/sample_003.json}
\lstinputlisting[language=json]{code/samples/sample_003.json}

\subsection{samples/sample\_004.json}\label{app:samples/sample_004.json}
\lstinputlisting[language=json]{code/samples/sample_004.json}

\subsection{samples/baltimore\_truss.json}\label{app:samples/baltimore_truss.json}
\lstinputlisting[language=json]{code/samples/baltimore_truss.json}

\section{Output Files}

\end{appendices}
